---
title: "NHP: tagged scenarios and site selections"
date: "Last updated: `r format(Sys.time(), '%d %b %Y at %H:%M')`"
output: html_document
---

```{r}
#| label: check-env-vars
#| results: "asis"
#| echo: false
#| message: false

required_env_vars <- c(
  "AZ_TENANT_ID",
  "AZ_STORAGE_CONTAINER_SUPPORT",
  "AZ_STORAGE_EP",
  "AZ_TABLE_EP",
  "NHP_ENCRYPT_KEY"
)

if (any(Sys.getenv(required_env_vars) == "")) {
  cat("One of the following environment variables was not set, so exiting \n\n")
  cat(paste("*", required_env_vars, collapse = "\n"), "\n\n")
  knitr::knit_exit()
}
```

```{r}
#| label: get-data
#| echo: false
#| message: false

source("R/azure.R")
source("R/wrangle.R")
source("R/table.R")
library(readr)

scheme_lookup <- Sys.getenv("AZ_STORAGE_CONTAINER_SUPPORT") |>
  get_container(container_name = _) |>
  get_scheme_lookup()

storage_table <- get_table()
entities <- storage_table |> AzureTableStor::list_table_entities()
results_table <- entities |>
  tibble::as_tibble() |>
  dplyr::rename(dataset = PartitionKey)
```

```{r}
#| label: prepare-tables
#| echo: false
#| message: false
runs_table <- tabulate_scenarios(results_table, scheme_lookup)
sites_table <- tabulate_sites(results_table, scheme_lookup)
```

---

## Purpose

Use these interactive tables to make sure that the correct scenarios and sites have been labelled for each scheme in the New Hospitals Programme (NHP). This will help ensure that products such as the outputs report and mitigator-comparison report will contain the correct information.

This page updates automatically once per week (see the publish date and time above), but is usually updated manually when new information is available. Please contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) if any of the information here needs to be changed.

## Scenarios

Check that the correct model scenarios have been tagged with the correct 'run stage' metadata. Contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) to ask for updates. Provide the scheme name, scenario name, app version and run stage (currently 'initial', 'intermediate', 'final report', or 'addendum report') and non-demographic growth (NDG) variant (1, 2 or 3).

```{r}
#| label: runs-table
#| echo: false
create_datatable_runs(runs_table)
```

## Sites

Check that the correct sites have been specified for the production of output reports. Contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) to ask for updates. Provide the scheme name, site codes and whether these apply differently depending on the activity type (A&E, inpatients and outpatients).

```{r}
#| label: sites-table
#| echo: false
create_datatable_sites(sites_table)
```

## Notes

There is functionality in the tables for you to:

- search and filter across the whole tables or column-by-column
- open the NHP Outputs app pre-loaded with the selected run
- download a CSV of the currently-filtered data

Be aware that:

- this page is intended primarily as a tool for the Data Science team's benefit
- it may not reflect the current up-to-the-moment 'truth' (check the 'last updated' datetime)
- it is not intended for purposes of governance, as schemes and model-relationship managers should keep their own records

Please contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) if any of the information here needs to be updated.
