---
title: "NHP: tagged model scenarios and schemes"
date: "last-modified"
date-format: D MMM YYYY HH:mm:ss
author:
  - name: The Data Science Team
    email: mlcsu.su.datascience@nhs.net
format:
  html:
    self-contained: true
    toc: true
    number-sections: false
    grid:
      body-width: 1000px
execute:
  echo: false
  message: false
  warning: false
---

```{r mess}
#| label: check-env-vars
#| results: "asis"

required_env_vars <- c(
  "AZ_TENANT_ID",
  "AZ_STORAGE_EP",
  "AZ_STORAGE_CONTAINER_RESULTS",
  "AZ_STORAGE_CONTAINER_SUPPORT",
  "NHP_ENCRYPT_KEY"
)

if (any(Sys.getenv(required_env_vars) == "")) {
  cat("One of the following environment variables was not set, so exiting \n\n")
  cat(paste("*", required_env_vars, collapse = "\n"), "\n\n")
  knitr::knit_exit() 
}
```

```{r}
#| label: prepare-tables

source("R/azure.R")
source("R/wrangle.R")
source("R/table.R")

container_results <- 
  Sys.getenv("AZ_STORAGE_CONTAINER_RESULTS") |> 
  get_container(container_name = _)

container_support <- 
  Sys.getenv("AZ_STORAGE_CONTAINER_SUPPORT") |> 
  get_container(container_name = _)

result_sets  <- get_nhp_result_sets(container_results)
scheme_lookup <- get_scheme_lookup(container_support)
runs_table  <- prepare_run_stage_runs(result_sets, scheme_lookup)

report_sites <- get_report_sites(container_support)
sites_table <- tabulate_sites(report_sites)
```

## Purpose

Use these interactive tables to make sure that the correct scenarios and sites have been labelled for each scheme in the New Hospital Programme. This will help ensure that products such as the outputs and mitigator-comparison reports will contain the correct information.

This page automatically updates (see the publish date and time above), but please contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) if any of the information here needs to be updated.

## Scenarios

Check that the correct model scenarios have been tagged with the correct 'run stage' metadata. Contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) to ask for updates. Provide the scheme name, scenario name, app version and run stage ('initial', 'intermediate' or 'final report') and non-demographic growth (NDG) variant (1 or 2).

```{r}
#| label: runs-table
create_datatable_runs(runs_table)
```

## Schemes

Check that the correct sites have been specified for the production of output reports. Contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) to ask for updates. Provide the scheme name, site codes and whether these apply differently depending on the activity type (A&E, inpatients and outpatients).

```{r}
#| label: sites-table
create_datatable_sites(sites_table)
```

## Notes

There is functionality for you to:

- search and filter across the whole tables or column-by-column
- open the NHP Outputs app pre-loaded with the selected run
- download a CSV of the currently-filtered data

Be aware that:

- this page is intended primarily as a tool for the Data Science team's benefit
- it may not reflect the current up-to-the-moment 'truth' (check the 'last updated' datetime)
- it is not intended for purposes of governance, as schemes and model-relationship managers should keep their own records

Please contact [the Data Science team](mailto:mlcsu.su.datascience@nhs.net) if any of the information here needs to be updated.
